
\section{Outreach}

\denseouterlist{

\entrymid[\textbullet]
{\textbf{Lead Organizer}, \href{https://astronomyontap.org/locations/las-vegas-nevada/}{Astronomy on Tap, Las Vegas}}{2022\textendash present}
{Helped organize the following events:} \\
\href{https://astronomyontap.org/event/astronomy-on-tap-las-vegas-xi/}{"Astronomy on Tap, Las Vegas XI"} (Mar. 5, 2024) \\
\href{https://astronomyontap.org/event/aot-las-vegas-10-10-3-var-100-years-of-variable-stars-extragalactic-astronomy-2/}{"VAR! 100 Years of Variable Stars \& Extragalactic Astronomy"} (Oct. 3, 2023) \\
\href{https://astronomyontap.org/event/astronomy-on-tap-las-vegas-8-journey-to-the-center-of-the-earth/}{"Journey to the Center of the Earth"} (Jun. 20, 2023) \\
\href{https://astronomyontap.org/event/astronomy-on-tap-las-vegas-7-universe-in-a-box-2/}{"Universe in a Box"} (Mar. 2, 2023) \\
\href{https://astronomyontap.org/event/aot-las-vegas-backyard-telescopes/}{"Backyard Telescopes"} (May 26, 2022) \\
{\href{https://astronomyontap.org/event/aot-las-vegas-the-horrors-of-black-holes-2/}{"The Horrors of Black Holes"}} (Oct. 27, 2022)

\entrymid[\textbullet]
{\textbf{Event Supervisor}, \href{https://www.nevadaso.org/}{Nevada Science Olympiad State Tournament}, \href{https://www.soinc.org/events/2023-division-b-events}{Division B (middle school)}}{2022\textendash\href{https://www.unlv.edu/news/unlvtoday/unlv-hosts-nevada-high-school-students-during-2023-nevada-science-olympiad}{2023}}
{Developed and administered written exams for the \href{https://www.soinc.org/solar-system-b}{Solar System event}}

\entrymid[\textbullet]
{\textbf{Judge}, \href{https://www.unlv.edu/sciences/science-fair}{Beal Bank USA Southern Nevada Regional Science \& Engineering Fair}}{2022\textendash2023}
{\href{https://www.unlv.edu/sciences/schools}{Elementary, middle}, and \href{https://www.unlv.edu/sciences/science-fair/high-school}{high school} divisions}

\entrymid[\textbullet]
{\textbf{Exhibit}, \href{https://www.unlv.edu/event/inquiry-iii-art-scientific-discovery}{Inquiry III: The Art of Scientific Discovery (UNLV College of Sciences)}}{Oct 2022}
{Submitted a display piece entitled ``Streaming Instability''}

\entrymid[\textbullet]
{\textbf{Assistant Organizer}, Neighborhood Star Party, Las Vegas, NV}{2022}
{Helped Prof. Jason Steffen organize the event at Sonoma at Summerlin by Coleman HOA} (Oct. 8)

}
